Visualization of Fractional Integrals

### 2019-03-05 fractional/CMJ style files/article-template.tex
added new integral

\section{xxx}
The fractional integral is defined as (need to be more explicit here). Need to add how it has come about... Start with a single integral, expand to the general case and then 
to a general $\alpha$. 
\begin{equation}
\frac{1}{\Gamma(\alpha)}\int_{0}^{t}f(\tau)(t-\tau)^{\alpha-1}~d\tau
\end{equation}

>>>>

\section{Riemann-Liouville Fractional Integral}
Let
\begin{equation}
If(x) := \int_0^x f(t) dt.
\end{equation}
If we apply the above operator in a repetative manner to $f$ we obtain the $n$th antiderivative of $f$ based at 0:
\begin{equation}
\label{eq:n_anti}
I^nf(x) = \int_0^x\int_0^{x_1}\cdots \int_0^{x_{n-1}}f(x_n)~dx_n\cdots dx_2 dx_1.
\end{equation}
Applying Cauchy's formula for repetative integration to the above $n$th antiderivative of $f$ helps us express the above $n$th antiderivative as a single integral. 
Applying Cauchy's formula to Equation~\ref{eq:n_anti} results in:
\begin{equation}
\label{eq:cauchy}
I^nf(x) = \frac{1}{(n-1)!}\int_0^x (x-t)^{n-1}f(t)~dt.
\end{equation}
As an example if $f(x)=x$ and $n=2$ then Equation~\ref{eq:cauchy} reduces to:
\begin{equation}
I^3f(x) = \int_0^x (x-t)t~dt = \frac{t^2x}{2} - \frac{t^3}{3} \Bigg |_0^x = \frac{x^3}{3!}.
\end{equation}
The definition in Equation~\ref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function:
\begin{equation}
\label{eq:frac_integral}
I^{\alpha}f(x) = \frac{1}{\Gamma(\alpha)}\int_0^x (x-t)^{\alpha-1}f(t)~dt.
\end{equation}
Equation~\ref{eq:frac_integral} is known as the Riemann-Liouville fractional integral of order $\alpha$.
\subsection{Examples}
If $f(x)=x$ and $n=3$ then Equation~\ref{eq:frac_integral} reduces to:
\begin{equation}
I^3f(x) = \frac{1}{2!} \int_0^x (x-t)^2t~dt = \frac{1}{2}\left[\frac{t^4}{4} - \frac{2t^3}{3}+\frac{t^2x^2}{2}\right] \Bigg |_0^x = \frac{x^4}{4!} 
\end{equation}

The fractional integral is defined as (need to be more explicit here). Need to add how it has come about... Start with a single integral, expand to the general case and then 
to a general $\alpha$. 
\begin{equation}
\frac{1}{\Gamma(\alpha)}\int_{0}^{t}f(\tau)(t-\tau)^{\alpha-1}~d\tau
\end{equation}
